Assessing Replication via P-values

### 2018-07-12 McNemar's Test/draft_mcnemars_ttest.Rmd
Made some edits

$$
H_0: \sum\limits_{j=1}^k P \Big ( \frac{|T_{1j}|}{\sqrt{v_{1j}}} \geq 1.96 |i \Big) P(i) = \sum\limits_{j=1}^k P \Big ( \frac{|T_{2j}|}{\sqrt{v_{2j}}} \geq 1.96 |i \Big) P(i)
$$

@@

$$
n_{01} = \sum\limits_{j=1}^k \mathbf{1} \Big \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96  \Big \rbrace \mathbf{1} \Big \lbrace \frac{|T_{2j}|}{\sqrt{v_{2j}}} \geq 1.96  \Big \rbrace \rightarrow \sum\limits_{j=1}^k \mathbf{1} \Big \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96 \Big \rbrace
$$
This implies that the McNemar's test statistic $X^2$  $\rightarrow$ $\sum\limits_{j=1}^k \mathbf{1} \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96 \rbrace$ as the replication sample sizes grow large. Let's assume that all $k$ original studies have 80% power to detect their true effect. Then, $X^2$ approaches $0.2k$ as the replication sample sizes increase. Recall that McNemar's test rejects if $X^2 > \chi^2_{[0.05,1]}$. In this instance, as long as $k>2$, McNemar's test will always reject despite the true effect sizes being identical for all $k$ study pairs.

@@

\newpage 
## Appendix

>>>>

$$
H_0: \sum\limits_{j=1}^k P \Big ( \frac{|T_{1j}|}{\sqrt{v_{1j}}} \geq 1.96 |j \Big) P(j) = \sum\limits_{j=1}^k P \Big ( \frac{|T_{2j}|}{\sqrt{v_{2j}}} \geq 1.96 |j \Big) P(j)
$$

@@

$$
n_{01} = \sum\limits_{j=1}^k \mathbf{1} \Big \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96  \Big \rbrace \mathbf{1} \Big \lbrace \frac{|T_{2j}|}{\sqrt{v_{2j}}} \geq 1.96  \Big \rbrace \rightarrow \sum\limits_{j=1}^k \mathbf{1} \Big \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96 \Big \rbrace
$$
This implies that the McNemar's test statistic $X^2 = \frac{(n_{10} - n_{01})^2}{n_{10} + n_{01}}$  $\rightarrow$ $\sum\limits_{j=1}^k \mathbf{1} \lbrace \frac{|T_{1j}|}{\sqrt{v_{1j}}} < 1.96 \rbrace$ as the replication sample sizes grow large. Let's assume that all $k$ original studies have 80% power to detect their true effect. Then, $X^2$ approaches $0.2k$ as the replication sample sizes increase. Recall that McNemar's test rejects if $X^2 > \chi^2_{[0.05,1]}$. In this instance, as long as $k \geq 20$, McNemar's test will always reject despite the true effect sizes being identical for all $k$ study pairs.

@@

## Appendix A: Reframing McNemar's Null Hypothesis

Recall that the null hypothesis for McNemar's test states that the marginal probabilities for each outcome are the same. That is, $H_0: p_{11} + p_{10} = p_{11} + p_{01}$ where $p_{11}$ is the proportion of $k$ study pairs in which both findings were significant, $p_{10}$ is the proportion of $k$ study pairs in which the original finding was significant and the replication finding was not, and $p_{01}$ is the proportion of $k$ study pairs in which the original finding was not sigificant and the replication finding was. Note that this is equivalent to the null hypothesis $p_{1+} = p_{+1}$ where $p_{1+}$ is the proportion of $k$ study pairs in which the original finding was significant and $p_{+1}$ is the proportion of $k$ study pairs in which the replication finding was significant. We can reformulate the null hypothesis in terms of the p-values of the original and replication studies as follows.

$$
\begin{aligned}
H_0&:  p_{1+} = p_{+1} \\
H_0&: \frac{1}{k}\sum\limits_{j=1}^k p_{1j} \leq 0.05 = \frac{1}{k}\sum\limits_{j=1}^k p_{2j} \leq 0.05

\end{aligned}
$$

## Appendix B: Agreement between McNemar's test and the \textit{t} test
